Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter

### 2021-02-05 reports/manuscript/cover_letter/cover_letter.tex
Change paper formatting to PLOS-CompBio

We are pleased to submit our manuscript entitled ``Multidimensional analysis
and detection of informative features in human brain white matter'' to Nature
Methods.

>>>>

We are pleased to submit our manuscript entitled ``Multidimensional analysis
and detection of informative features in human brain white matter'' to
\emph{PLOS Computational Biology}.
